Convergence Studies and Effective Alphas for Disks with Gravitational Instabilities. \\ I. The Constant Cooling Case

### 2010-12-08 Paper_1.tex
Tom's changes w/ figures working.
	modified:   Paper_1.tex

\begin{figure}
%\plotone{figures/qcompareres.eps}
\plotone{figures/qcompareres.pdf}
\caption{Toomre Q distribution versus radius for each of the four resolutions at t $\sim$ 18 ORPs}
\label{fig:Final_Q}
\end{figure}

\begin{figure}
%\plotone{figures/Figure_1.eps}
\plotone{figures/Figure_1.pdf}
\caption
{
Midplane disk densities at $t \sim 18$ ORPs for simulations with 64, 128, 256 and 512 azimuthal grid elements.
The simulations differ only in the number of  azimuthal zones used in the calculations.  Densities out of the plane, along an azimuthal cut through the disk, are displayed below the face-on views.  The color scale is  logarithmic, and axis units are AU. 
}
\label{fig:DensityPlots}
\end{figure}
\newpage

\begin{figure}
%\plotone{figures/Figure_3.eps}
\plotone{figures/Figure_3.pdf}
\caption
{
The logarithm of the amplitudes for the global Fourier components of the non-axisymmetric density structure plotted for different $m$-values. Notice that the components with the highest global amplitudes are those with low $m$-values.  
}
\label{fig:Am_vs_log_m}
\end{figure}

\begin{figure}
%\plotone{figures/Power_Extrapolation.eps}
\plotone{figures/Power_Extrapolation.pdf}
\caption
{
Convergence of fractional power.  The $x$-axis represents
the azimuthal ``spacing'' between grid points,  normalized such that spacing of the $l_{max}$ = 512 grid
equals unity.
The $y$-axis displays the fraction of the total power in the low-order ($m = $ 2--7) Fourier modes. 
Also plotted is the Richardson Extrapolation for the asymptotic value  
$\langle A_{2-7} \rangle / \langle A_{tot} \rangle = 0.42$ as the grid spacing goes to zero.  
}
\label{fig:Power_Extrap}
\end{figure}

\begin{figure}
%\plotone{figures/Torque_Array.eps}
\plotone{figures/Torque_Array.pdf}
\caption
{
Time-averaged torques summed over a number of low-order modes, 
$\sum_1^n \langle {\rm \bf C}_{Z(n)} \rangle$, where $n = $1,  2, 3, 4, and 5, along
with the total time-averaged gravitational torque,
$\langle {\rm \bf C}_{Ztot} \rangle = \sum_1^n \langle {\rm \bf C}_{Z(n)} \rangle$, where $n =  l_{max}/2$,
as a function of radius and azimuthal resolution. 
The scale of the $y$-axis in each subplot is the same, with the exception of the $l_{max} = 64$ simulation, 
where the scale is doubled.  
Note that the total gravitational torque is smaller for simulations run at higher azimuthal resolutions, and the total torque is dominated by low-order modes for all azimuthal resolutions. 
}
\label{fig:Torque_array}
\end{figure}

@@

\begin{figure}
%\plotone{figures/Figure_2.eps}
\plotone{figures/Figure_2.pdf}
\caption
{Effective $\alpha$'s, time-averaged between 12 and 18 ORPs, for simulations performed with four different azimuthal grid resolutions. Dashed lines show values of $\alpha$ predicted by  \citet{gammie2001}  for the
strongly self-gravitating limit (lower line) and the non-self-gravitating limit
(upper line).
The dotted line at $\log(\alpha) = -1.22$ represents the maximum stress a disk subject to constant cooling
can maintain without fragmenting, as  proposed by  \cite{rice2005}.
}
\label{fig:alpha_v_radius}
\end{figure}
\newpage

\begin{figure}
%\plotone{figures/Alpha_variations_stack512.eps}
\plotone{figures/Alpha_variations_stack512.pdf}
\caption
{
Time variability of $\alpha$ as a function of radius.  Here $\alpha$ is normalized to its averaged value between at $t = 14$ and 18 ORP.  The orbital period at each radius is provided by the length of the bracketed line shown above its radius label. 
}
\label{fig:alpha_stack}
\end{figure}

>>>>

\begin{figure}\label{Final_Q}
\plotone{figures/Figure1.eps}
\caption{Toomre Q distribution versus radius for each of the four resolutions at t $\sim$ 18 ORPs}
\end{figure}

\begin{figure}\label{fig:DensityPlots}
%\plotone{figures/Figure2.eps}
\caption
{
Midplane disk densities at $t \sim 18$ ORPs for simulations with 64, 128, 256 and 512 azimuthal grid elements.
The simulations differ only in the number of  azimuthal zones used in the calculations.  Densities out of the plane, along an azimuthal cut through the disk, are displayed below the face-on views.  The color scale is  logarithmic, and axis units are AU. 
}
\end{figure}
\newpage

\begin{figure}\label{fig:Am_vs_log_m}
%\plotone{figures/Figure3.eps}
\caption
{
The logarithm of the amplitudes for the global Fourier components of the non-axisymmetric density structure plotted for different $m$-values. Notice that the components with the highest global amplitudes are those with low $m$-values.  
}
\end{figure}

\begin{figure}
%\plotone{figures/Figure4.eps}
\caption
{
Convergence of fractional power.  The $x$-axis represents
the azimuthal ``spacing'' between grid points,  normalized such that spacing of the $l_{max}$ = 512 grid
equals unity.
The $y$-axis displays the fraction of the total power in the low-order ($m = $ 2--7) Fourier modes. 
Also plotted is the Richardson Extrapolation for the asymptotic value  
$\langle A_{2-7} \rangle / \langle A_{tot} \rangle = 0.43$ as the grid spacing goes to zero.  
}
\end{figure}

\begin{figure}
%\plotone{figures/Figure5.eps}
\caption
{
Torque Array}
\end{figure}

@@

\begin{figure}
\label{fig:alpha_v_radius}
%\plotone{figures/Figure6.eps}
\caption
{Effective $\alpha$'s for the $t_{cool} =$ 2 ORP, $\gamma = 5/3$, $\Sigma \sim r^{ -1}$ disk, averaged between 12 and 18 ORPs, for four different different azimuthal grid resolutions, given by the number of azimuthal grid-points Lmax. The parallel dashed lines show the predictions of Gammie (2001) for $\alpha$ (upper: strongly self-gravitating limit, lower: non-self-gravitating limit), while the dashed line at $\log(\alpha) = -1.22$ represents the maximum stress a disk can maintain without fragmenting (Rice et al. 2005) . 
}
\end{figure}
\newpage

\begin{figure}
%\plotone{figures/Figure7.eps}
\caption
{Alpha variations.}
\end{figure}
